---
title: "Training-Workshop on Building Resilient Communities: DRRMT Training and Livelihood Formation for Women's Organization"
date: "December 22, 2025"
author:
  - "Summary of Evaluation"
  - "Barangay Paitan"
format: 
  docx:
    reference-doc: template.docx
editor: visual
execute:
  echo: FALSE
  warning: FALSE
  message: FALSE
---

```{r}
#| label: load-packages

library(tidyverse)
library(readr)
library(ggstats)
library(labelled)
library(forcats)
```

```{r}
#| label: load-data

data1 <- read_csv(
  "data/eval-paitan-vista-alegre-12222325.csv",
  col_types = cols(
    q1 = col_factor(
      levels = c("1", "2", "3", "4", "5"),
      ordered = T
    ),
    q2 = col_factor(
      levels = c("1", "2", "3", "4", "5"),
      ordered = T
    ),
    q3 = col_factor(
      levels = c("1", "2", "3", "4", "5"),
      ordered = T
    ),
  )
) |>
  filter(Barangay == "Paitan") |>
  select(q1:q3)
```

# Ratings

The training was evaluated by `r nrow(data1)` participants. Most of the ratings for relevance, timeliness, and overall rating are excellent. The percentage of ratings for each item is shown in @fig-items. Relevance, timeliness, and overall rating has a rating of excellent with means `r round(mean(as.numeric(data1$q1)), 2)`, `r round(mean(as.numeric(data1$q2)), 2)`, and `r round(mean(as.numeric(data1$q3)), 2)` respectively.

```{r}
#| label: fig-items
#| fig-cap: "Percentage of Ratings"
#| fig-width: 6.5

data1 |>
  mutate(
    q1 = fct_recode(
      q1,
      "Poor" = "1",
      "Fair" = "2",
      "Satisfactory" = "3",
      "Very Satisfactory" = "4",
      "Excellent" = "5"
    ),
    q2 = fct_recode(
      q2,
      "Poor" = "1",
      "Fair" = "2",
      "Satisfactory" = "3",
      "Very Satisfactory" = "4",
      "Excellent" = "5"
    ),
    q3 = fct_recode(
      q3,
      "Poor" = "1",
      "Fair" = "2",
      "Satisfactory" = "3",
      "Very Satisfactory" = "4",
      "Excellent" = "5"
    )
  ) |>
  gglikert(
    variable_labels = c(
      q1 = "Relevance",
      q2 = "Timeliness",
      q3 = "Overall Rating"
    ),
    cutoff = 0,
    add_totals = FALSE
  )
```

# Other training/activity/technical service needed

During the event, participants expressed the following interests in other training, activity, and technical services needed:

-   **Livelihood and Entrepreneurship Development:** Business-related trainings, women and business–related trainings, and livelihood programs addressing women’s needs.

-   **Agriculture and Food Production:** Rice production and pest management training, Bread making and baking activities.

-   **Technical and Vocational Skills:** Dressmaking and garment production, electrical servicing, and automotive.

The repeated mention of dress making and bread making highlights a strong interest in these areas.

# Comments / Suggestions on How to Improve Our Services

Participants generally expressed positive feedback particularly appreciating the competence of the speakers and the quality of instruction.

**Positive Observations:**

Participants commended the presence of skilled speakers and trainers, noting that the instructors were effective and capable of facilitating learning.

**Suggestions for Improvement:**

-   **Discipline and Timeliness:** Participants emphasized the importance of unity, discipline, and early or timely conduct of activities to ensure smooth implementation.

-   **Capacity-Building Needs:** There were repeated requests for more training opportunities, particularly in dressmaking.

-   **Continuous Development:** Participants suggested sustained engagement through continuous review of performance and follow-up activities to further enhance skills and learning outcomes.

Overall, the feedback indicates satisfaction with the trainers and program delivery, alongside a strong demand for additional trainings and continuous improvement initiatives.
