---
title: "Intersection of Gender, Livelihood, and Disaster Risk Reduction Management"
subtitle: "Barangay Vista Alegre, Bayombong, Nueva Vizcaya"
date: February 19, 2025
date-format: long
author: Summary of Evaluation
format: 
  docx:
    reference-doc: template.docx
editor: visual
execute:
  echo: FALSE
  warning: FALSE
  message: FALSE
---

```{r}
#| label: load-packages

library(tidyverse)
library(readr)
library(ggstats)
library(labelled)
library(forcats)
```

```{r}
#| label: load-data

data1 <- read_csv(
  "data/vista-alegre.csv",
  col_types = cols(
    q1 = col_factor(
      levels = c("1", "2", "3", "4", "5"),
      ordered = T
    ),
    q2 = col_factor(
      levels = c("1", "2", "3", "4", "5"),
      ordered = T
    ),
    q3 = col_factor(
      levels = c("1", "2", "3", "4", "5"),
      ordered = T
    ),
    gender =  col_factor(
      levels = c("Male", "Female")
    )
  )
)
```

# Ratings

The training was evaluated by 31 participants. Most of the ratings for relevance, timeliness, and overall rating are excellent. The percentage of ratings for each item is shown in @fig-items. Relevance, timeliness, and overall rating has a rating of excellent with means `r round(mean(as.numeric(data1$q1)), 2)`, `r round(mean(as.numeric(data1$q2)), 2)`, and `r round(mean(as.numeric(data1$q3)), 2)` respectively.

```{r}
#| label: fig-items
#| fig-cap: "Percentage of Ratings"
#| fig-width: 6.5

data1 |>
  select(q1:q3) |>
  mutate(
    q1 = fct_recode(
      q1,
      "Poor" = "1",
      "Fair" = "2",
      "Satisfactory" = "3",
      "Very Satisfactory" = "4",
      "Excellent" = "5"
    ),
    q2 = fct_recode(
      q2,
      "Poor" = "1",
      "Fair" = "2",
      "Satisfactory" = "3",
      "Very Satisfactory" = "4",
      "Excellent" = "5"
    ),
    q3 = fct_recode(
      q3,
      "Poor" = "1",
      "Fair" = "2",
      "Satisfactory" = "3",
      "Very Satisfactory" = "4",
      "Excellent" = "5"
    )
  ) |>
  gglikert(
    variable_labels = c(
      q1 = "Relevance",
      q2 = "Timeliness",
      q3 = "Overall Rating"
    ),
    cutoff = 0,
    add_totals = FALSE
  )
```

# Other training/activity/technical service needed

During the event, participants expressed interest in a range of additional training, activities, and technical services to enhance their skills and livelihood opportunities. The identified needs include:

- **Livelihood and Skills Training:**
Handicraft making, urban gardening, mushroom production, vermi composting, dressmaking, sewing, bookkeeping, carpentry, and masonry.

- **Food-related Trainings:**
Food processing (frequently mentioned), bread and pastry making, cake and pastry making, and additional trainings on food preservation and processing.

- **Technical and Vocational Skills:**
Glass cutting, driving, and fish pond management (including handling techniques).

The repeated mention of food processing and dressmaking highlights a strong interest in these areas.

# Comment/suggestions on how to improve our services

Participants expressed appreciation for the program, frequently offering thanks and congratulatory remarks. Key feedback includes:

- **Positive Acknowledgments:**
Multiple participants conveyed gratitude (e.g., “Thank you,” “More power,” “Ang galing!”) and commended the organizers for a well-delivered and informative session (“Perfect explanation,” “Congratulations!”).

- **Suggestions for Improvement:**

    - **Scheduling Concerns:** A participant suggested starting earlier to accommodate everyone’s availability and ensure full participation.

    - **Training Needs:** Several requested more training sessions, especially in their barangay, highlighting a desire for continued capacity-building efforts.

    - **Sustained Engagement:** Follow-ups were recommended to ensure continuity and to deepen learning outcomes from the initial session.

Overall, the feedback reflects strong participant engagement, satisfaction with the current program, and eagerness for more targeted training opportunities.
